---
output:
  word_document: default
  html_document: default
---
r---
title: "R Notebook"
output: html_notebook
---
Just some 4D visualisation for further understanding


```{r}
rm(list=ls())
library(neuralnet)
library(tidyr)
library(ggplot2)
library(dplyr)

setwd("Z:/Projects/<CensoredPath>/ML/Code/RAnalysen")
source("NeuralNetworkAnalysis.R")

load("nn_model_4.Rdata")
load("Z:/Projects/<CensoredPath>/ML/Code/RAnalysen/shapley_computed.Rdata")
nn_kat <- nn_model_4
```



Preparing the data

```{r}
 weights_2 <- weights_second
 weights_1 <- weights_first
```



# Calculate how the neurons are distributed:

```{r fig.height=9, fig.width=9}
library(corrplot)
library(ggpubr)
hist1<-ggplot(kat_hidden) + geom_histogram(aes(hidden_1),fill="#1AA7EC")+
  xlab(" Activities for Hidden Neuron 1") +ylab("Count")
hist2<-ggplot(kat_hidden) + geom_histogram(aes(hidden_2),fill="#1AA7EC")+
  xlab(" Activities for Hidden Neuron 2") +ylab("Count")
hist3<-ggplot(kat_hidden) + geom_histogram(aes(hidden_3),fill="#1AA7EC")+
  xlab(" Activities for Hidden Neuron 3") +ylab("Count")
hist4<-ggplot(kat_hidden) + geom_histogram(aes(hidden_4),fill="#1AA7EC")+
  xlab(" Activities for Hidden Neuron 4") +ylab("Count")
 
 figure_hist <- ggarrange(hist1,hist2,hist3,hist4, ncol = 2, nrow = 2)
 figure_hist
 
```


```{r fig.height=6, fig.width=6}
plot(figure_hist)
```



```{r}
setwd("Z:/Projects/<CensoredPath>/ML/Code/RAnalysen")
write.table(cor(kat_hidden[,c("hidden_1","hidden_2","hidden_3","hidden_4")]), file="./exports4/corNeuron.csv")

 corrplot(cor(kat_hidden[,c("hidden_1","hidden_2","hidden_3","hidden_4")]), method="circle", number.cex = 1.2) +   theme(legend.position="bottom",legend.title.align=0.5, legend.background=element_rect(size=0.2,colour="grey")) 
```



```{r fig.height=4, fig.width=4}

 corrplot(cor(kat_hidden[,c("hidden_1","hidden_2","hidden_3","hidden_4")]), method="circle", number.cex = 1.2) +   theme(legend.position="bottom",legend.title.align=0.5, legend.background=element_rect(size=0.2,colour="grey")) 
```

```{r fig.height=3, fig.width=3}

 corrplot(cor(kat_hidden[,c("hidden_1","hidden_2","hidden_3","hidden_4")]), method="circle", number.cex = 1.2) +   theme(legend.position="bottom",legend.title.align=0.5, legend.background=element_rect(size=0.2,colour="grey")) 
```


```{r fig.height=2, fig.width=2}

 corrplot(cor(kat_hidden[,c("hidden_1","hidden_2","hidden_3","hidden_4")]), method="circle", number.cex = 1.2) +   theme(legend.position="bottom",legend.title.align=0.5, legend.background=element_rect(size=0.2,colour="grey")) 
```
# Extraction for the Second layer


```{r}
test <- mtcars %>%
  group_by(cyl) %>%
  summarise(mean = mean(disp))
```


Alternative approach: Neuron 1-3 are binary, afterwads linear

```{r}

library(ggpubr)


mul_matrix<-data.frame(x=1)
mul<-c(1,0)
for(i in 1:3)
{ 
  mul_matrix<-crossing(mul_matrix,mul)
  colnames(mul_matrix)<-1:(i+1)
}

order_classes <- sort(c("Staying in School","Dual VET","School-based VET"))
rand<-as.data.frame(0:1000/1000)
mul_matrix <- crossing(mul_matrix,rand)
colnames(mul_matrix) = c("BIAS","H1","H2", "H3", "H4")
mul_matrix$type = as.factor(paste0(mul_matrix$H1,mul_matrix$H2,mul_matrix$H3))
mul_matrix$Classification<-as.factor(apply(as.matrix(mul_matrix[,1:5]) %*% as.matrix(weights_2),1,which.max))
mul_matrix$Classification<-as.factor(order_classes[mul_matrix$Classification])

thresholds <- mul_matrix %>% group_by(mul_matrix$Classification,mul_matrix$type) %>% summarise(test = min(H4))
write.table(thresholds, file="./exports4/thresholds.csv")


g1<-ggplot() + geom_bar(data=mul_matrix, aes( x=type, fill=Classification), position="fill", alpha=0.5) + theme(plot.title = element_text(hjust = 0.5))+ scale_fill_manual(values = c("Staying in School" = "#65AD8D","Dual VET" = "#D8787B", "School-based VET" = "#1AA7EC")) + 
theme(legend.position="bottom",legend.title.align=0.5, legend.margin= margin(r=1, l=1, t=0.5, b=0.5, unit="cm"),  legend.background=element_rect(size=0.2,colour="grey"), legend.key.width= unit(1, "in")) +
    guides(fill=guide_legend(title.position="bottom",label.position = "bottom")) +
 ylab("Activation of Hidden Neuron 4") +
 xlab("Configuration of Activities for Hidden Neuron 1-3") 


g1
```

```{r fig.height=8, fig.width=6}
plot(g1)
```

```{r fig.height=6, fig.width=6}
plot(g1)
```

```{r fig.height=4, fig.width=6}
plot(g1)
```

Show missclassification of Rule 2
```{r fig.height=16, fig.width=12}

kat_hidden$type <- as.factor(paste0(as.numeric(kat_hidden$hidden_1>0.5),as.numeric(kat_hidden$hidden_2>0.5),as.numeric(kat_hidden$hidden_3>0.5)))

g2<-ggplot() + 
  geom_bar(data=mul_matrix, aes( x=type, fill=Classification), position="fill", alpha=0.6) +
  theme(plot.title = element_text(hjust = 0.5))+ theme(legend.position="bottom")  + 
  geom_jitter(data=kat_hidden[kat_hidden$train=="Dual VET",], aes(x=type, y=hidden_4, colour=train), shape=16, width=0.35) +
    scale_fill_manual(values = c("Staying in School" = "#65AD8D","Dual VET" = "#D8787B", "School-based VET" = "#1AA7EC")) +
    scale_colour_manual(values = c("Staying in School" = "#65AD8D","Dual VET" = "#D8787B", "School-based VET" = "#1AA7EC")) +
theme(legend.position="bottom",legend.title.align=0.5, legend.margin= margin(r=1, l=1, t=0.5, b=0.5, unit="cm"),  legend.background=element_rect(size=0.2,colour="grey"), legend.key.width= unit(1, "in"))+    guides(fill=guide_legend(title.position="bottom",label.position = "bottom")) + guides(shape=FALSE)+ guides(colour=FALSE)+
 ylab("Activation of Hidden Neuron 4") +
  xlab("Configuration of Activities for Hidden Neuron 1-3") 


g3<-ggplot() + 
  geom_bar(data=mul_matrix, aes( x=type, fill=Classification), position="fill", alpha=0.6) +
  theme(plot.title = element_text(hjust = 0.5))+ theme(legend.position="bottom")  + 
  geom_jitter(data=kat_hidden[kat_hidden$train=="School-based VET",], aes(x=type, y=hidden_4, colour=train), shape=16, width=0.35) +
    scale_fill_manual(values = c("Staying in School" = "#65AD8D","Dual VET" = "#D8787B", "School-based VET" = "#1AA7EC")) +
    scale_colour_manual(values = c("Staying in School" = "#65AD8D","Dual VET" = "#D8787B", "School-based VET" = "#1AA7EC")) +
theme(legend.position="bottom",legend.title.align=0.5, legend.margin= margin(r=1, l=1, t=0.5, b=0.5, unit="cm"),  legend.background=element_rect(size=0.2,colour="grey"), legend.key.width= unit(1, "in"))+    guides(fill=guide_legend(title.position="bottom",label.position = "bottom")) + guides(shape=FALSE)+ guides(colour=FALSE)+
 ylab("Activation of Hidden Neuron 4") +
  xlab("Configuration of Activities for Hidden Neuron 1-3") 


g4<-ggplot() + 
  geom_bar(data=mul_matrix, aes( x=type, fill=Classification), position="fill", alpha=0.6) +
  theme(plot.title = element_text(hjust = 0.5))+ theme(legend.position="bottom")  + 
  geom_jitter(data=kat_hidden[kat_hidden$train=="Staying in School",], aes(x=type, y=hidden_4, colour=train), shape=16, width=0.35) +
    scale_fill_manual(values = c("Staying in School" = "#65AD8D","Dual VET" = "#D8787B", "School-based VET" = "#1AA7EC")) +
    scale_colour_manual(values = c("Staying in School" = "#65AD8D","Dual VET" = "#D8787B", "School-based VET" = "#1AA7EC")) +
theme(legend.position="bottom",legend.title.align=0.5, legend.margin= margin(r=1, l=1, t=0.5, b=0.5, unit="cm"),  legend.background=element_rect(size=0.2,colour="grey"), legend.key.width= unit(1, "in"))+    guides(fill=guide_legend(title.position="bottom",label.position = "bottom")) + guides(shape=FALSE)+ guides(colour=FALSE) +
 ylab("Activation of Hidden Neuron 4") +
  xlab("Configuration of Activities for Hidden Neuron 1-3") 

 figure <- ggarrange(g3,g2,g4,ncol = 1, nrow = 3, common.legend=TRUE, legend="bottom", legend.grob=get_legend(g4))
 figure

```

```{r fig.height=16, fig.width=9}
plot(figure)
```


```{r fig.height=12, fig.width=6}
plot(figure)
```

# Compute Share of right Classifications by Second layer
```{r}

lay1stat <- data.frame(cbind(1,kat_hidden$hidden_1>0.5,kat_hidden$hidden_2>0.5,kat_hidden$hidden_3>0.5,kat_hidden$hidden_4))
lay1stat$train <- kat_hidden$train
colnames(lay1stat) = c("BIAS","H1","H2", "H3", "H4", "train")
lay1stat$Classification <- apply(as.matrix(lay1stat[,1:5]) %*% as.matrix(weights_2),1,which.max)

lay1stat$Classification<-as.factor(order_classes[lay1stat$Classification])

mean(lay1stat$Classification==lay1stat$train)


```


# Rule Extraction for the first layer

```{r}
library(stringr)
weights_normal <- as.data.frame(t(weights_1))
weights_normal$Bias <- weights_normal$Bias + weights_normal$female + weights_normal$mig_background_0 + weights_normal$parents_academic_edu_0 + weights_normal$last_diploma_type_1 + weights_normal$parents_school_edu_1
weights_normal$parents_academic_edu_1 <- weights_normal$parents_academic_edu_1 - weights_normal$parents_academic_edu_0
weights_normal$male <- weights_normal$male - weights_normal$female
weights_normal$mig_background_1 <- weights_normal$mig_background_1 - weights_normal$mig_background_0
weights_normal$parents_school_edu_0 <- weights_normal$parents_school_edu_0 - weights_normal$parents_school_edu_1
weights_normal$parents_school_edu_2 <- weights_normal$parents_school_edu_2 - weights_normal$parents_school_edu_1
weights_normal$last_diploma_type_0<- weights_normal$last_diploma_type_0 - weights_normal$last_diploma_type_1
weights_normal$last_diploma_type_2<- weights_normal$last_diploma_type_2 - weights_normal$last_diploma_type_1
weights_normal<-subset(weights_normal,select=-c(female,mig_background_0,parents_academic_edu_0,last_diploma_type_1,parents_school_edu_1))
weights_norm <- t(weights_normal)
neuron_1 <- as.data.frame(weights_norm[,1])
neuron_2 <- as.data.frame( weights_norm[,2])
neuron_3 <- as.data.frame( weights_norm[,3])
neuron_4 <- as.data.frame(weights_norm[,4])
# Just a hack to keep rownames
neuron_1$test <- 1
neuron_2$test <- 1
neuron_3$test <- 1
neuron_4$test <- 1
row.names(neuron_1) <- row.names(weights_norm)
row.names(neuron_2) <- row.names(weights_norm)
row.names(neuron_3) <- row.names(weights_norm)
row.names(neuron_4) <- row.names(weights_norm)



library(dplyr)
library(Hmisc)
library(stringr)
#neuron_1_selected <- rownames(neuron_1[abs(neuron_1[,1]) > 0.25 * min(abs(neuron_1[order(neuron_1$`weights_norm[, 1]`),1][1]), abs(neuron_1[order(-neuron_1$`weights_norm[, 1]`),1][1])),])
#neuron_2_selected <- rownames(neuron_2[abs(neuron_2[,1]) > 0.25 * min(abs(neuron_2[order(neuron_2$`weights_norm[, 2]`),1][1]), abs(neuron_2[order(-neuron_2$`weights_norm[, 2]`),1][1])),])
#neuron_3_selected <- rownames(neuron_3[abs(neuron_3[,1]) > 0.25 * min(abs(neuron_3[order(neuron_3$`weights_norm[, 3]`),1][1]), abs(neuron_3[order(-neuron_3$`weights_norm[, 3]`),1][1])),])
#neuron_4_selected <- rownames(neuron_4[abs(neuron_4[,1]) > 0.25 * min(abs(neuron_4[order(neuron_4$`weights_norm[, 4]`),1][1]), abs(neuron_4[order(-neuron_4$`weights_norm[, 4]`),1][1])),])

neuron_1_selected <- rownames(neuron_1[abs(neuron_1[,1]) >  mean(abs(neuron_1[order(neuron_1$`weights_norm[, 1]`),1])),])
neuron_2_selected <- rownames(neuron_2[abs(neuron_2[,1]) >  mean(abs(neuron_2[order(neuron_2$`weights_norm[, 2]`),1])),]) 
neuron_3_selected <- rownames(neuron_3[abs(neuron_3[,1]) >  mean(abs(neuron_3[order(neuron_3$`weights_norm[, 3]`),1])),]) 
neuron_4_selected <- rownames(neuron_4[abs(neuron_4[,1]) > mean(abs(neuron_4[order(neuron_4$`weights_norm[, 4]`),1])),])


neuron_1<-round(neuron_1[neuron_1_selected,c(1,2)],2)
neuron_2<-round(neuron_2[neuron_2_selected,c(1,2)],2) 
neuron_3<-round(neuron_3[neuron_3_selected,c(1,2)],2) 
neuron_4<-round(neuron_4[neuron_4_selected,c(1,2)],2)

neuron_1_table <- neuron_1[order(neuron_1[,1]),]
rownames(neuron_1_table)<- gsub("_", "_",  rownames(neuron_1_table))
colnames(neuron_1_table)<-c("Weights","delete")
neuron_1_table 

neuron_2_table <- neuron_2[order(neuron_2[,1]),]
rownames(neuron_2_table)<- gsub("_", "_",  rownames(neuron_2_table))
colnames(neuron_2_table)<-c("Weights","delete")
neuron_2_table 

neuron_3_table <- neuron_3[order(neuron_3[,1]),]
rownames(neuron_3_table)<- gsub("_", "_",  rownames(neuron_3_table))
colnames(neuron_3_table)<-c("Weights","delete")
neuron_3_table 

neuron_4_table <- neuron_4[order(neuron_4[,1]),]
rownames(neuron_4_table)<- gsub("_", "_",  rownames(neuron_4_table))
colnames(neuron_4_table)<-c("Weights","delete")
neuron_4_table 

write.table(neuron_1_table, file="./exports4/n1_table.csv")
write.table(neuron_2_table, file="./exports4/n2_table.csv")
write.table(neuron_3_table, file="./exports4/n3_table.csv")
write.table(neuron_4_table, file="./exports4/n4_table.csv")



```

## Compute share of right classifications by 1 and 2
```{r}
kat_hidden$Bias <- 1
kat_hidden<-data.frame(kat_hidden)


kat_hidden$rule1 <- #test_3[2]>0.5
 ((as.matrix(data.frame(kat_hidden[,rownames(neuron_1)]))) %*% (as.numeric(neuron_1[,1])) > 0 )

kat_hidden$rule2 <- #test_3[2]>0.5
 ((as.matrix(data.frame(kat_hidden[,rownames(neuron_2)]))) %*% (as.numeric(neuron_2[,1])) > 0 )

kat_hidden$rule3 <- #test_3[2]>0.5
 ((as.matrix(data.frame(kat_hidden[,rownames(neuron_3)]))) %*% (as.numeric(neuron_3[,1])) > 0 )

kat_hidden$rule4 <-  (as.matrix(data.frame(kat_hidden[,rownames(neuron_4)])) %*% as.numeric(neuron_4[,1]))
kat_hidden$rule4 <- 1/ (1+exp(-kat_hidden$rule4))

lay1stat <- data.frame(cbind(1,kat_hidden$rule1,kat_hidden$rule2,kat_hidden$rule3,kat_hidden$rule4))
lay1stat$train <- kat_hidden$train
colnames(lay1stat) = c("BIAS","H1","H2", "H3", "H4", "train")
lay1stat$Classification <- apply(as.matrix(lay1stat[,1:5]) %*% as.matrix(weights_2),1,which.max)

lay1stat$Classification<-as.factor(order_classes[lay1stat$Classification])
kat_hidden$ruleClassification <- lay1stat$Classification

mean(lay1stat$Classification==lay1stat$train)

```

```{r}
print("Right Choices:")
mean(kat_hidden$train == kat_hidden$ruleClassification)

b0t0 <- sum(kat_hidden$ruleClassification==classes[1] & kat_hidden$train==classes[1]) 
b1t0 <- sum(kat_hidden$ruleClassification==classes[2] & kat_hidden$train==classes[1]) 
b2t0 <- sum(kat_hidden$ruleClassification==classes[3] & kat_hidden$train==classes[1]) 

b0t1<-sum(kat_hidden$ruleClassification==classes[1] & kat_hidden$train==classes[2]) 
b1t1<-sum(kat_hidden$ruleClassification==classes[2] & kat_hidden$train==classes[2]) 
b2t1<-sum(kat_hidden$ruleClassification==classes[3] & kat_hidden$train==classes[2]) 

b0t2<-sum(kat_hidden$ruleClassification==classes[1] & kat_hidden$train==classes[3]) 
b1t2<-sum(kat_hidden$ruleClassification==classes[2] & kat_hidden$train==classes[3]) 
b2t2<- sum(kat_hidden$ruleClassification==classes[3] & kat_hidden$train==classes[3]) 


real0<-c(b0t0,b1t0,b2t0)
real1<-c(b0t1,b1t1,b2t1)
real2<-c(b0t2,b1t2,b2t2)

pr_matrix<-cbind(real0,real1,real2)
rownames(pr_matrix)<-classes
print("")
print("Absolute Classifications ")

pr_matrix

print("")
print("Real 0,1,2")
t0<-sum(kat_hidden$train==classes[1])
t1<-sum(kat_hidden$train==classes[2])
t2<-sum(kat_hidden$train==classes[3])
t0
t1
t2

print("")
print("Prediction 0,1,2")
b0<-sum(kat_hidden$ruleClassification==classes[1])
b1<-sum(kat_hidden$ruleClassification==classes[2])
b2<-sum(kat_hidden$ruleClassification==classes[3])
b0 
b1 
b2

train<-c(t0,t1,t2)
best<-c(b0,b1,b2)

print("")
print("relative to classification ")
pr_matrix1<-pr_matrix /best
pr_matrix1

print("")
print("relative to classified")

pr_matrix2<-t(t(pr_matrix) / train)
pr_matrix2


write.table(pr_matrix, file="./exports4/pr_matrix_rules.csv")
write.table(pr_matrix1, file="./exports4/pr_matrix1_rules.csv")
write.table(pr_matrix2, file="./exports4/pr_matrix2_rules.csv")
```

Show missclassification of Rule 2
```{r fig.height=16, fig.width=12}

kat_hidden$typer <- as.factor(paste0(as.numeric(kat_hidden$rule1),as.numeric(kat_hidden$rule2),as.numeric(kat_hidden$rule3)))

g2<-ggplot() + 
  geom_bar(data=mul_matrix, aes( x=type, fill=Classification), position="fill", alpha=0.6) +
  theme(plot.title = element_text(hjust = 0.5))+ theme(legend.position="bottom")  + 
  geom_jitter(data=kat_hidden[kat_hidden$train=="Dual VET",], aes(x=typer, y=hidden_4, colour=train), shape=16, width=0.35) +
    scale_fill_manual(values = c("Staying in School" = "#65AD8D","Dual VET" = "#D8787B", "School-based VET" = "#1AA7EC")) +
    scale_colour_manual(values = c("Staying in School" = "#65AD8D","Dual VET" = "#D8787B", "School-based VET" = "#1AA7EC")) +
theme(legend.position="bottom",legend.title.align=0.5, legend.margin= margin(r=1, l=1, t=0.5, b=0.5, unit="cm"),  legend.background=element_rect(size=0.2,colour="grey"), legend.key.width= unit(1, "in"))+    guides(fill=guide_legend(title.position="bottom",label.position = "bottom")) + guides(shape=FALSE)+ guides(colour=FALSE)+
 ylab("Activation of Hidden Neuron 4") +
  xlab("Configuration of Activities for Hidden Neuron 1-3") 


g3<-ggplot() + 
  geom_bar(data=mul_matrix, aes( x=type, fill=Classification), position="fill", alpha=0.6) +
  theme(plot.title = element_text(hjust = 0.5))+ theme(legend.position="bottom")  + 
  geom_jitter(data=kat_hidden[kat_hidden$train=="School-based VET",], aes(x=typer, y=hidden_4, colour=train), shape=16, width=0.35) +
    scale_fill_manual(values = c("Staying in School" = "#65AD8D","Dual VET" = "#D8787B", "School-based VET" = "#1AA7EC")) +
    scale_colour_manual(values = c("Staying in School" = "#65AD8D","Dual VET" = "#D8787B", "School-based VET" = "#1AA7EC")) +
theme(legend.position="bottom",legend.title.align=0.5, legend.margin= margin(r=1, l=1, t=0.5, b=0.5, unit="cm"),  legend.background=element_rect(size=0.2,colour="grey"), legend.key.width= unit(1, "in"))+    guides(fill=guide_legend(title.position="bottom",label.position = "bottom")) + guides(shape=FALSE)+ guides(colour=FALSE)+
 ylab("Activation of Hidden Neuron 4") +
  xlab("Configuration of Activities for Hidden Neuron 1-3") 


g4<-ggplot() + 
  geom_bar(data=mul_matrix, aes( x=type, fill=Classification), position="fill", alpha=0.6) +
  theme(plot.title = element_text(hjust = 0.5))+ theme(legend.position="bottom")  + 
  geom_jitter(data=kat_hidden[kat_hidden$train=="Staying in School",], aes(x=typer, y=hidden_4, colour=train), shape=16, width=0.35) +
    scale_fill_manual(values = c("Staying in School" = "#65AD8D","Dual VET" = "#D8787B", "School-based VET" = "#1AA7EC")) +
    scale_colour_manual(values = c("Staying in School" = "#65AD8D","Dual VET" = "#D8787B", "School-based VET" = "#1AA7EC")) +
theme(legend.position="bottom",legend.title.align=0.5, legend.margin= margin(r=1, l=1, t=0.5, b=0.5, unit="cm"),  legend.background=element_rect(size=0.2,colour="grey"), legend.key.width= unit(1, "in"))+    guides(fill=guide_legend(title.position="bottom",label.position = "bottom")) + guides(shape=FALSE)+ guides(colour=FALSE) +
 ylab("Activation of Hidden Neuron 4") +
  xlab("Configuration of Activities for Hidden Neuron 1-3") 

 figure <- ggarrange(g3,g2,g4,ncol = 1, nrow = 3, common.legend=TRUE, legend="bottom", legend.grob=get_legend(g4))
 figure

```

```{r fig.height=16, fig.width=9}
plot(figure)
```


```{r fig.height=12, fig.width=6}
plot(figure)
```

# Aggregate wrong and right clasisfications per District


```{r}

district_stat <- kat_hidden %>% group_by(reg_industry_area,reg_unemployed,reg_urban_permeation) %>% summarise(
                                       num_obs=n(),       
                                       num_school=sum(train=="Staying in School"),
                                       num_dual=sum(train=="Dual VET"),
                                       num_sbvet=sum(train=="School-based VET"),
                                       num_school_right=sum(train=="Staying in School" & ruleClassification=="Staying in School"),
                                       num_dual_right=sum(train=="Dual VET"  & ruleClassification=="Dual VET"),
                                       num_sbvet_right=sum(train=="School-based VET" & ruleClassification=="School-based VET"),
                                       ShareRight=mean(train==ruleClassification)) %>% arrange(ShareRight)                          

write.table(district_stat, file="./exports4/district_stat.csv")
                                                                                                     
district_stat <- district_stat[district_stat$num_obs>1,]
write.table(district_stat, file="./exports4/district_stat_2.csv")
```

```{r}

```



# Simulate some inputs according to the orginal distribution



set.seed(8004)
results <- vector(length=2)
sym_data<-data.frame(NULL)

for(i in 1:10000)
{
  
single_obs <- as.data.frame(t(c(1,runif(23))))
single_obs[,13:24] <- 0
single_obs[,sample(13:15,1)] <- 1
single_obs[,sample(16:17,1)] <- 1
single_obs[,sample(18:19,1)] <- 1
single_obs[,sample(20:22,1)] <- 1
single_obs[,sample(23:24,1)] <- 1

colnames(single_obs)<-row.names(weights_1)

#Calculate results from matrix
test <- as.matrix(single_obs) %*% as.matrix(weights_1)
test_2 <- 1/ (1+exp(-test))
test_3 <- c(1,test_2)
result<-which.max(test_3 %*% as.matrix(weights_2))

n1 <- #test_3[2]>0.5
  (as.numeric(single_obs[,rownames(neuron_1)]) %*% (as.numeric(neuron_1[,1]))) > 0 

n2 <- #test_3[3]>0.5
  (as.numeric(single_obs[,rownames(neuron_2)]) %*% (as.numeric(neuron_2[,1]))) > 0 

n3 <- #test_3[4]>0.5
  (as.numeric(single_obs[,rownames(neuron_3)]) %*% (as.numeric(neuron_3[,1]))) > 0 


n4 <- #test_3[5]>0.5
  max(0,min((as.numeric(single_obs[,rownames(neuron_4)]) %*% (as.numeric(neuron_4[,1])))/4 + 0.5,1))


n5 <- #test_3[6]>0.5
   max(0,min((as.numeric(single_obs[,rownames(neuron_5)]) %*% (as.numeric(neuron_5[,1])))/4 + 0.5,1))

neurons <- as.data.frame(t(c(1,n1,n2,n3,n4,n5)))
neurons$result <- as.factor(apply(  (t(as.matrix(as.numeric(neurons))) %*% as.matrix(weights_2[1:6,]))   ,1,which.max))
neurons$nn <- as.factor(result)
colnames(test_2)<-c("N1", "N2", "N3", "N4", "N5")
neurons<-cbind(test_2,neurons)
sym_data<-rbind(sym_data,neurons)                          
}

mean(sym_data$result == sym_data$nn)
sym_data <- sym_data[sym_data$result != sym_data$nn,]

